### 2016-12-22 thesis/latex/thesis.tex
Add diffusion figure script and Why do cells need motor transport? section.

\textbf{ATP} Adenosine triphosphate is a small organic molecule which very spontaneously breaks apart into ADP and a phosphate. This reaction is used to power many energy-requiring mechanisms within the cell. This reaction has a $\Delta G^\circ \approx -36 kJ/mol$ at physiological conditions \ref{ATPenergy}.\\\\
\textbf{Protein} Dynein is a protein, or long chain of amino acids linked together and folded into a particular shape.

\subsubsection{Why do cells need motor transport?}
Cells are structures with high organization in time and space. 
Cells are organized, heretogenous structures which respond quickly to their environments. This means that cells require a mechanism for rapidly moving cargo, and moving cargo to precise locations within the cell. This can be a challenge, since cells are fairly large compared to the proteins which compose them \textbf{is it also a challenge because its hard to get precise positions within a cell?}. A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter. In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2) \textbf{((is this the best way to cite this?))}, a $10^3$ factor difference in size.\\

Diffusion, or random motion of molecules due to collisions with solvent (i.e. Brownian motion), is one possible means cells could use to transport cargo. Diffusion has two problems: it is slow and nondirected. The expected distance covered for one-dimensional Brownian motion after time t was found by Einstein to be \textbf{cite here}:

@@

where D is the diffusion constant (flesh this out). The $\sqrt{t}$ scaling of diffusion contrasts with the linear scaling of motor transport.

This ties in a lot to the previous section. I originally thought of putting the <x> vs T diffusion/
motor plot in the introduction, but maybe it would be better here. Not sure.\\

>>>>

\textbf{ATP} Adenosine triphosphate is a small organic molecule which very spontaneously breaks apart into ADP and a phosphate. This reaction is used to power many energy-requiring mechanisms within the cell. This reaction has a $\Delta G^\circ \approx -36 kJ/mol$ at physiological conditions \ref{ATPenergy}.\\\\
\textbf{Protein} Dynein is a protein, or long chain of amino acids linked together and folded into a particular shape.\\

\subsubsection{Why do cells need motor transport?}
Cells are organized, heretogenous structures which respond quickly to their environments. This means that cells require a mechanism for rapidly moving components to precise locations within the cell. This can be a challenge, since cells are fairly large compared to the proteins which compose them. A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter. In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2) \textbf{((is this the best way to cite this?))}, a $10^3$ factor difference in size.\\

Diffusion, or random motion of molecules due to collisions with solvent (i.e. Brownian motion), is one possible means cells could use to transport biomolecules. Diffusion has two problems: it is slow and nondirected. The expected distance covered for one-dimensional Brownian motion after time t was found by Einstein to be \textbf{cite here}:

@@

where D is the diffusion constant describing the diffusability of the biomolecule. For a medium-sized (140kD, 1D = weight of H atom) protein with a diffusion constant $D = .2 \mu m^2/s$ \cite{diffusionconstants}, it would take about a month to travel across a millimeter-sized cell. In contrast, it would take dynein, which travels at roughly 100nm/s \cite{weihongpaper}, a much more reasonable three hours to do the same.

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
  \caption{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
  \label{diffusion_vs_dynein}
\end{figure}

Another advantage of motor transport is that microtubules can be highly specific in their location in the cell, as in chromosomal segregation, where dynein walks on MTs bound directly to chromosomes. Diffusion is an inherently random process, and so could never provide such spatial specificity.\\
